---
title: "DANL 200: Introduction to Data Analytics<br>Project"
subtitle: "Quarto Template<br><br>" 
author: 
  - name: Jeremy Sun
    affiliations:
      - name: SUNY Geneseo
  
   
  - <br>
date: "`r Sys.Date()`"

format: 
  html:
    toc: true
    number-sections: false
    code-fold: false       # https://quarto.org/docs/output-formats/html-code.html
    code-summary: "Show the code"
    code-tools: true
    highlight-style: espresso # atom-one tango espresso

execute: 
  echo: true
  eval: true
  warning: false
  message: false
  fig-width: 9
  
---


```{r setup, include = FALSE}
library(tidyverse)
library(hrbrthemes)
library(skimr)

```


```{r}
oj <- read_csv('https://bcdanl.github.io/data/dominick_oj.csv')
nvars <- format(round(ncol(oj), 0), 
                nsmall=0, 
                big.mark=",") 
nobs <- format(round(nrow(oj), 0), 
                nsmall=0, 
                big.mark=",")
```

- Here is the paged table using `rmarkdown::paged_table()` with the `results = 'asis'` chunk option.

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(oj) 
```


```{r}
theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )

```

```{r}
billboard <- read_csv('https://bcdanl.github.io/data/billboard.csv')
rmarkdown::paged_table(billboard)
```



##Q!A

--Describe how the distribution of rating varies across week 1, week 2, and week 3 using the faceted histogram.

```{r}
ggplot(billboard) +
  geom_histogram(aes(x= wk1))
```

### Wit Facet

```{r}
q1a <- billboard %>% 
  pivot_longer(col = wk1:wk76,
               names_to = "week",
               values_to = "rating" ) %>% 
  filter(week %in% c('wk1','wk2','wk3' ) )  



```

```{r}


```


##Q1B


--Which artist(s) have the most number of tracks in billboard data.frame?

--Do not double-count an artist’s tracks if they appear in multiple weeks.



##Q2A

--Make ny_pincp longer.

##Q2B

--Provide both (1) ggplot code and (2) a simple comment to describe how overall the yearly trend of NY counties’ average personal incomes are.


##Q3A
--Keep only the following three variables, date, countriesAndTerritories, and cases.

Then make a wide-form data.frame of covid whose variable names are from countriesAndTerritories and values are from cases.

Then drop the variable date.



##Q3B

Use the wide-form data.frame of covid to find the top 10 countries in terms of the correlation between their cases and the USA case.
Use cor(data.frame), which returns a matrix.
Then convert it to data.frame using as.data.frame(matrix)


